Foraging: The Triumphant Return

### 2022-04-25 manuscript.tex
adding methods section

\begin{figure}[H]
\includegraphics[width=12 cm]{Figures/qjep_preds.png}
\caption{This is a figure. Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.\label{fig1}}
\end{figure}

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=12 cm]{Figures/qjep_preds.png}
\caption{Posterior probabilities for target selections during a visual foraging task. Each dot represents...}
\end{figure}
